LDATS Rodents Example

### 2019-07-08 doc/rodents-example.Rmd
simplification of the control lists
The control lists have been made easier to interact with. Primarily, the arguments that previously required `LDA_controls_list`, `TS_controls_list`, or `LDA_TS_controls_list` inputs now take general `list` inputs (so  `LDA_TS` does not need to have a nested set of control functions). Each control list is passed through a function (`LDA_set_control`, `TS_control`, or `LDA_TS_control`) to set any non-input values to their defaults. This also allows the removal of those controls list class definitions. ([addresses issue 130](https://github.com/weecology/LDATS/i

We use `LDA_controls_list())` to pass controls to the LDA function. In this case, we can set `quiet = TRUE` to make the model run quietly.

```{r lda_set, eval =F}
lda_model_set <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:5),
                         nseeds = 10,
                         control = LDA_controls_list(quiet = TRUE))

@@

`LDA_set()` returns a list of LDA models. We use `select_LDA()` to identify the best number of topics and choice of seed from our set of models. By default, we will choose models based on minimum AIC. To use different selection criteria, define the appropriate functions and specify them using `LDA_controls_list(measurer = [measurer function], selector = [max, min, etc])`.

@@

```{r ts on lda, eval = F}
changepoint_models <- TS_on_LDA(LDA_models = selected_lda_model, 
                                document_covariate_table = rodents$document_covariate_table,
                                formulas = ~ sin_year + cos_year,
                                nchangepoints = c(0:1), 
                                weights = document_weights(rodents$document_term_table),
                                timename = "newmoon",
                                control = TS_controls_list(nit = 1000))

@@

We can adjust options for both TS functions using `TS_controls_list()`. For a full list see `?TS_controls_list`. Here we illustrate adjusting the number of ptMCMC iterations - the default is 10000, but it is convenient to use fewer iterations for code development.

@@

`select_TS()` will identify the best-fit changepoint model of the models from `TS_on_LDA()`. As with `select_LDA()`, we can adjust the `measurer` and `selector` using `TS_controls_list()`.

@@

Finally, we can perform an entire LDATS analysis, including all of the above steps, using the `LDA_TS()` function and passing options to the LDA and TS functions using `LDA_TS_controls_list()`.

```{r lda_ts, eval = F}
lda_ts_results <- LDA_TS(document_term_table = rodents$document_term_table,
                         document_covariate_table = rodents$document_covariate_table,
                         nseeds = 10, 
                         topics = 2:5,
                         formulas = ~ sin_year + cos_year,
                         nchangepoints= 0:1,
                         weights = document_weights(rodents$document_term_table),
                         timename = "newmoon",
                         control = LDA_TS_controls_list(
                           TS_control = TS_controls_list(nit = 1000)))
```

>>>>

We use the `control` argument to pass controls to the LDA function via a `list`. In this case, we can set `quiet = TRUE` to make the model run quietly.

```{r lda_set, eval =F}
lda_model_set <- LDA_set(document_term_table = rodents$document_term_table,
                         topics = c(2:5),
                         nseeds = 10,
                         control = list(quiet = TRUE))

@@

`LDA_set()` returns a list of LDA models. We use `select_LDA()` to identify the best number of topics and choice of seed from our set of models. By default, we will choose models based on minimum AIC. To use different selection criteria, define the appropriate functions and specify them by passing `list(measurer = [measurer function], selector = [max, min, etc])` to the `control` argument.

@@

```{r ts on lda, eval = F}
changepoint_models <- TS_on_LDA(LDA_models = selected_lda_model, 
                                document_covariate_table = rodents$document_covariate_table,
                                formulas = ~ sin_year + cos_year,
                                nchangepoints = c(0:1), 
                                timename = "newmoon",
                                weights = document_weights(rodents$document_term_table),
                                control = list(nit = 1000))

@@

We can adjust options (default settings can be seen using `TS_control()`) for both TS functions by passing a list to the `control` argument. For a full list see `?TS_control`. Here we illustrate adjusting the number of ptMCMC iterations - the default is 10000, but it is convenient to use fewer iterations for code development.

@@

`select_TS()` will identify the best-fit changepoint model of the models from `TS_on_LDA()`. As with `select_LDA()`, we can adjust the `measurer` and `selector` functions using the `control` argument list.

@@

Finally, we can perform an entire LDATS analysis, including all of the above steps, using the `LDA_TS()` function and passing options to the LDA and TS functions as a `list` to the `control` argument. The default is for `LDA_TS` to weight the time series model based on the document sizes, so we do not need to tell it to do so.

```{r lda_ts, eval = F}
lda_ts_results <- LDA_TS(data = rodents,
                         nseeds = 10, 
                         topics = 2:5,
                         formulas = ~ sin_year + cos_year,
                         nchangepoints= 0:1,
                         timename = "newmoon",
                         control = list(nit = 1000))
```
